SubsidyExplorer - Step 4: Apply proposal 'definitions' to vessel list

### 2020-04-13 scripts/02_vessel_list.Rmd
still updating

We then need to get total catches and revenues per fishing KWh by flag and FAO region, as well as by flag. We first will assign catch rates for FAO region/flag combinations that appear in both the GFW and FAO data. For FAO region/flag combinations that don't appear in the FAO data, we will allocate the remainder?

>>>>

We then need to get total catches and revenues per fishing kWh by flag and FAO region, as well as by flag. We first will assign catch rates for FAO region/flag combinations that appear in both the GFW and FAO data. For FAO region/flag combinations that don't appear in the FAO data, we will assign the overall rate by flag state.

### 2020-04-13 scripts/04_subsidy_reform_definitions.Rmd
still updating

# Directories for the output files generated by this script
results_dir <- here::here("results", "5-vessel-list-policy-definitions/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}

>>>>

# Directories for the output files generated by this script
results_dir <- here::here("results", "04_subsidy_reform_definitions/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
